\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Chandler Swift} % Your name
\address{320-296-4833 --- chandler@chandlerswift.com}
\address{11105 Carver Court, Burnsville, MN 55337}

\begin{document}

\begin{rSection}{Education}

    {\bf University of Minnesota Duluth} \hfill {\em August 2015--December 2019} 
    \\ B.S. in Computer Science, with a minor in Mathematics
    \\ Cum Laude (GPA 3.89), Dean's list 9/9 semesters

\end{rSection}

\begin{rSection}{Experience}

    \begin{rSubsection}{Pearson VUE: \textnormal{Associate Cloud Engineer}}{\em Dec 2019--Present}{}{}
        \item Implemented code in Ansible and Terraform to deploy and configure infrastructure as code.
        \item Worked with Jenkins and Azure DevOps to insure continuous integration of that infrastructure.
        \item Used Zabbix and Splunk to monitor deployed resources, and alert on failures.
        \item Provided support to dev teams, troubleshooting and fixing apps deployed in Kubernetes.
    \end{rSubsection}

    \begin{rSubsection}{Bravo Reporting Systems: \textnormal{PHP Software Developer}}{\em May 2015--Dec 2019}{}{}
        \item Developed a PHP/Laravel web application to provide action item
            tracking and reporting.
        \item Provided customer-facing end-user support for technical issues.
        \item Implemented continuous integration system to provide automated testing,
            compilation, and deployment.
    \end{rSubsection}

    \begin{rSubsection}{Dash360: \textnormal{.NET Software Developer}}{\em May 2019--Dec 2019}{}{}
        \item Developed a C\# software-as-a-service platform for collecting and
            reporting project management data.
    \end{rSubsection}

    \begin{rSubsection}{Lockheed Martin Aeronautics: \textnormal{Cybersecurity Engineering Intern}}{\em May--August 2018}{}{}
        \item Created proof-of-concept blockchain demo for message provenance across internal communication buses.
        \item Designed a penetration testing exercise to increase security awareness of non-technical executives.
    \end{rSubsection}

%
%    \begin{rSubsection}{Lockheed Martin Aeronautics: \textnormal{Cybersecurity Engineering Intern}}{\em June--August 2017}{}{}
    %    \item Streamlined Excel report generation using automation to cut 2hr weekly tasking to <5min.
    %    \item Prototyped web-based tracking system which provided weekly reporting as well as automatically generated dashboard stats to replace Excel spreadsheet (Laravel, LAMP stack).
    %    \iitem Constructed proof-of-concept USB keystroke injection attack using covert hardware.
    %    \item Analyzed historical data in manager’s absence and presented requested trend data to upper management.
    %    \item Configured and deployed hardware for a new lab to be used in training exercises.
    %    \item Mentored another intern in programming and basics of penetration testing.
%    \end{rSubsection}

\end{rSection}

\begin{rSection}{Projects}

    \begin{rSubsection}{Do This and Nothing More \textnormal{(Summer 2019)}}{\href{https://github.com/UMDLARS/dtanm}{github.com/UMDLARS/dtanm}}{}\\
        \item Architected, designed, and developed a Flask web app frontend and
            git/Python backend for scoring user-developed and submitted
            applications against a known-good piece of software.
        \item Implemented Docker sandboxing of all user-submitted code, caching layers to
            improve performance, and an extensive user interface for interacting
            with the framework through a browser.
        \item Refined design by soliciting and incorporating feedback from
            two semesters' Computer Security classes.
    \end{rSubsection}

    \begin{rSubsection}{UMD CYLGame Framework \textnormal{(Summer 2019)}}{\href{https://github.com/UMDLARS/CYLGame}{github.com/UMDLARS/CYLGame}}{}\\
        \item Designed competitions to run on UMD's CYLGame framework.
        \item Added documentation and designed helper tools to ease
            development of further competitions.
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Skills}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Programing Languages & Strong Python, C, Go; some Javascript, C++, Java, C\# \\
        Tools                & Linux, Git, Ansible, Terraform, Jenkins, Zabbix, Splunk \\
        Platforms            & Azure, AWS, Kubernetes, Azure DevOps, GitHub \\
    \end{tabular}

\end{rSection}

%\begin(rSection){Additional notes}
%    \item Organist at many churches; most recently at Pilgrim
%    \item Accompanist for LSYC, helped work with kids
%    \item SPL, Eagle Scout
%    \item Freelance web developer: Jaeckel, etc
%    \item Concert Chorale President
%\end{rsection}

\centering\textit{References available upon request.}

\end{document}
